Project Ideas and Notes

### 2023-10-25 corridor_docs/thesis_ideas.Rmd
made a change to test committing
added citation

### _Notes from conversation with Julian:_

1. Low-hanging fruit: Effect of connectivity on (a) species and functional group diversity and abundance
1. Next level: Movement & Dispersal. There are large areas of forest where it is possible to capture beetles for Mark-Release-Recapture (MRR) experiments.
1. Higher-risk, Higher reward (even if they don't go in MS, can be set-up for potential PHD projects): Experiments on Ecosystem Services

@@

+ @WOS:000178929600002: "56% of individuals were captured in the continuous forest, 29% in the mosaic habitat and 15% in the forest fragments"

@@

1. Species List & Keys for Dung Beetles of the Southeastern US
1. Any previous work done on dung beetles in Southeastern US
1. List of Equipment and Tools needed
+ Dung beetle traps
+ alcohol
+ bait

@@

<!-- Good stuff in here: -->
<!-- https://link.springer.com/article/10.1007/s10531-017-1299-7 -->
<!-- https://www.sciencedirect.com/science/article/pii/S1470160X19303486 -->

1. Paragraph 1: Habitat Fragmentation is a common feature of most human dominated landscapes, and Corridors are thought to be an important means of connecting these isolated patches.
1. Paragraph 2: It is predicted that Corridors will increase diversity of connected patches. Summary of findings. However, because of this gap in research, it remains unclear how_____.
1. Paragraph 3: Part of the reason we havbe this gap is that few studis have assessed dispersal of animals through corridors from one patch to another. I know...crazy. Lots of studies have assessed movement, but few of these have actually done so in cases where one patch is conncected to another. 
1. Paragraph 4: Dung Beetles are a critical and divese functional group that is often used as an indicator species. I am proposing to use a large-scale experiement of connectd and unconnected patches to assess how corridors shape dung beetle diversity and movement. Specifically, i will address the following questions:

@@

Are corridors predicted to enhance diversity in connected patches? What is the mechanism>? A certain species groups are predicted to drive this change in diversity - rare species, larger species, specialists, particular function groups, better fliers, etc.? (_Note: "Corridors" = Riparian strips, living fences, linear fragments, etc._)

@@

@@

> Prediction: Species diversity is greater in connected patches than isolated ones (due to the greater representation of rare species) 
> OR
> Prediction: Diversity of _______ (e.g., specialists, foraging strategy X, etc.) is greater in connected patches, but the Diversity of ________ (e.g., generalists, foraging strategy Y) will be the similar in both.
> OR
> The diversity is similar, but the community composition changes to one dominated by specialists instead of generalists

@@

>>>>

### *Notes from conversation with Julian:*

1.  Low-hanging fruit: Effect of connectivity on (a) species and functional group diversity and abundance
2.  Next level: Movement & Dispersal. There are large areas of forest where it is possible to capture beetles for Mark-Release-Recapture (MRR) experiments.
3.  Higher-risk, Higher reward (even if they don't go in MS, can be set-up for potential PHD projects): Experiments on Ecosystem Services

@@

-   @WOS:000178929600002: "56% of individuals were captured in the continuous forest, 29% in the mosaic habitat and 15% in the forest fragments"

@@

1.  Species List & Keys for Dung Beetles of the Southeastern US
2.  Any previous work done on dung beetles in Southeastern US
3.  List of Equipment and Tools needed

-   Dung beetle traps
-   alcohol
-   bait

@@

<!-- Good stuff in here: -->

<!-- https://link.springer.com/article/10.1007/s10531-017-1299-7 -->

<!-- https://www.sciencedirect.com/science/article/pii/S1470160X19303486 -->

1.  Paragraph 1: Habitat Fragmentation is a common feature of most human dominated landscapes, and Corridors are thought to be an important means of connecting these isolated patches.
2.  Paragraph 2: It is predicted that Corridors will increase diversity of connected patches. Summary of findings. However, because of this gap in research, it remains unclear how\_\_\_\_\_.
3.  Paragraph 3: Part of the reason we havbe this gap is that few studis have assessed dispersal of animals through corridors from one patch to another. I know...crazy. Lots of studies have assessed movement, but few of these have actually done so in cases where one patch is conncected to another.
4.  Paragraph 4: Dung Beetles are a critical and divese functional group that is often used as an indicator species. I am proposing to use a large-scale experiement of connectd and unconnected patches to assess how corridors shape dung beetle diversity and movement. Specifically, i will address the following questions:

@@

Are corridors predicted to enhance diversity in connected patches? What is the mechanism\>? A certain species groups are predicted to drive this change in diversity - rare species, larger species, specialists, particular function groups, better fliers, etc.? (*Note: "Corridors" = Riparian strips, living fences, linear fragments, etc.*)

@@

-   **Diversity increases:** [@WOS:000399235300014]

@@

> Prediction: Species diversity is greater in connected patches than isolated ones (due to the greater representation of rare species) OR Prediction: Diversity of \_\_\_\_\_\_\_ (e.g., specialists, foraging strategy X, etc.) is greater in connected patches, but the Diversity of \_\_\_\_\_\_\_\_ (e.g., generalists, foraging strategy Y) will be the similar in both. OR The diversity is similar, but the community composition changes to one dominated by specialists instead of generalists

@@

#practice push
